\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\title{Snapshot Objectives}
\author{LAPD1 Development Team}
\date{\today}

\begin{document}

\maketitle

\section*{Snapshot 1 Objectives}
\begin{itemize}[label=--]
    \item Define the initial system architecture and design strategy.
    \item Establish key functional modules: frontend, backend, NLP processing.
    \item Confirm primary integration requirements with Box.com and AWS.
    \item Prepare the foundational SRS and SDD drafts.
\end{itemize}

\section*{Snapshot 2 Objectives}
\begin{itemize}[label=--]
    \item Implement the document upload and validation features.
    \item Integrate OCR for scanned transcript handling.
    \item Set up the basic NLP pipeline for named entity recognition.
    \item Deploy initial testing framework for data ingestion.
\end{itemize}

\section*{Snapshot 3 Objectives}
\begin{itemize}[label=--]
    \item Complete implementation of entity extraction and misconduct detection.
    \item Finalize integration with Box.com and Salesforce.
    \item Expand the user interface to support flagged results and annotations.
    \item Conduct system and integration tests.
\end{itemize}

\section*{Snapshot 4 Objectives}
\begin{itemize}[label=--]
    \item Finalize the UI with dashboard, reporting, and export features.
    \item Optimize NLP models for performance and accuracy.
    \item Prepare the system for deployment within LACPD infrastructure.
    \item Submit final revisions to SRS, SDD, and README documentation.
\end{itemize}

\end{document}
